Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-23 paper.tex
minor edits

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three
parts. Hypercoercions make this structure explicit: a hypercion $c$ is
either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or contains
three parts: a head, middle, and tail, as defined in
\figref{fig:hypercoercion}.
\begin{itemize}
\item The head $h$ is either a projection or the identity,
\item the middle $m$ involves coercions that preserve a type
  constructor, i.e., coercions between function, pair, sum types, and
  unit types, and
\item the tail $t$ is either an injection, a failure, or the identity.
\end{itemize}
There is a one-to-one correspondence between middle coercions and type
constructors.  We generalize shallow-consistency to middles $m \smile
m$ in the obvious way.

Subsection~\ref{sec:ld-hc} defines functions that construct
\lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines the
\lazyUD\ counterparts.  The functions that apply hypercoercions to
values are defined later in
Section~\ref{sec:hypercoercion-correctness}, after we introduce the
space-efficient machine and its definition of values in
Section~\ref{sec:framework}.

>>>>

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three
parts. Hypercoercions make this structure explicit: a hypercion $c$ is
either $\hyperCoercionI$, the identity cast for $\TOOdyn$, or it contains
three parts: a head, middle, and tail, as defined in
\figref{fig:hypercoercion}.
\begin{itemize}
\item The head $h$ is either a projection or the identity,
\item the middle $m$ involves coercions that preserve a type
  constructor, i.e., coercions between function, pair, sum types, and
  unit types, and
\item the tail $t$ is either an injection, a failure, or the identity.
\end{itemize}
There is a close correspondence between middle coercions and type
constructors.  We generalize shallow-consistency to middles $m \smile
m$ in the obvious way.

Subsection~\ref{sec:ld-hc} defines the $id$, $seq$, and $cast$
functions that construct
\lazyD\ hypercoercions. Subsection~\ref{sec:lud-hc} defines the
\lazyUD\ counterparts.  The functions that apply hypercoercions to
values are defined later in
Section~\ref{sec:hypercoercion-correctness}, after we introduce the
space-efficient machine and its definition of values in
Section~\ref{sec:framework}.
